Tracing the Meta-Level: PyPy's JIT Compiler

### 2009-03-31 talk/icooolps2009/paper.tex
fix an XXX

XXX write somewhere that we will be predominantly occupied with bytecode
interpreters
XXX write somewhere that one problem of using tracing JITs for dynamic languages
is that dynamic languages have very complex bytecodes

@@

The tracing JIT of the PyPy project is atypical in that it is not applied to the
user program, but to the interpreter running the user program. In this section
we will explore what problems this brings, and how to solve them (at least
partially). This means that there are two interpreters involved, and we need
terminology to distinguish them. On the one hand, there is the interpreter that
the tracing JIT uses to perform tracing. This we will call the \emph{tracing
interpreter}. On the other hand, there is the interpreter that is running the
users programs, which we will call the \emph{language interpreter}. The program
that the language interpreter executes we will call the \emph{user program}
(from the point of view of a VM author, the "user" is a programmer using the
VM).

>>>>

XXX write somewhere that one problem of using tracing JITs for dynamic languages
is that dynamic languages have very complex bytecodes

@@

The tracing JIT of the PyPy project is atypical in that it is not applied to the
user program, but to the interpreter running the user program. In this section
we will explore what problems this brings, and how to solve them (at least
partially). This means that there are two interpreters involved, and we need
terminology to distinguish them. On the one hand, there is the interpreter that
the tracing JIT uses to perform tracing. This we will call the \emph{tracing
interpreter}. On the other hand, there is the interpreter that is running the
users programs, which we will call the \emph{language interpreter}. In the
following, we will assume that the language interpreter is bytecode-based. The
program that the language interpreter executes we will call the \emph{user
program} (from the point of view of a VM author, the "user" is a programmer
using the VM).
